COVID19 - Forecast and predictions using a time dependent SEIR model

### 2020-03-14 draft_analysis_Italy.Rmd
Add home page, navigation and theme

```{r setup, include=FALSE}
rm(list=ls())
###import italian dataset updated 10 March 2020
dat_csv<-read.csv("https://raw.githubusercontent.com/pcm-dpc/COVID-19/master/dati-andamento-nazionale/dpc-covid19-ita-andamento-nazionale.csv",header=T)
days<-dim(dat_csv)[1]
dat_csv$t<-1:days

@@

r0.predict<-beta.predict
r0.predict[,c(1,3:5)]<-r0.predict[,c(1,3:5)]*14
# plot the points (actual observations), regression line, and confidence interval
p <- ggplot(r0.predict, aes(date,beta_vec))
p <- p + geom_point() +labs(x="time from t0",y="R0 value") 
p <- p + geom_line(aes(date,fit))
p <- p + geom_ribbon(aes(ymin=lwr,ymax=upr), alpha=0.3)
p
```

>>>>

```{r setup, include=FALSE}
rm(list=ls())
###import italian dataset updated 13 March 2020
dat_csv<-read.csv("https://raw.githubusercontent.com/pcm-dpc/COVID-19/master/dati-andamento-nazionale/dpc-covid19-ita-andamento-nazionale.csv",header=T)
days<-dim(dat_csv)[1]
dat_csv$t<-1:days
names(dat_csv)
```

@@

r0.predict<-beta.predict
r0.predict[,c(1,3:5)]<-r0.predict[,c(1,3:5)]*14
# plot the points (actual observations), regression line, and confidence interval
p <- ggplot(r0.predict, aes(date,beta_vec))
p <- p + geom_point() +labs(x="Date",y="R0 value") 
p <- p + geom_line(aes(date,fit))
p <- p + geom_ribbon(aes(ymin=lwr,ymax=upr), alpha=0.3)
p
```
